### 2018-06-18 dissertation/1-intro/chapter1.tex
Updated chapters 1 and 2

These features are discovered by tracing analogies with social networks.
There might be groups of nodes which meet each other with a predictable frequency and at predictable intervals, for example vehicles which belong to family members, neighbors or work colleagues.
By considering such features, TruMan allows the formation of strong trust relationships,  which in turn facilitate the discovery of malicious members of the network.

>>>>

These features are discovered by tracing analogies with social networks.
For example, certain groups of nodes might come into communication range of each other with predictable frequency, such as vehicles which belong to family members, neighbors or work colleagues as their owners perform their daily activities.
By considering such features, TruMan allows the formation of strong trust relationships,  which in turn facilitate the discovery of malicious members of the network.

### 2018-06-18 dissertation/2-complexnetworks/chapter2.tex
Updated chapters 1 and 2

\chapter{Complex Networks}
\label{chap:complexnetworks}

@@

Complex networks can describe many systems which are observed in nature and society through a collection of \textit{vertices} (or \textit{nodes}) and \textit{edges} \citep{newmannetworks}.
They can be comprised of palpable components (such as computers and cables), somewhat abstract entities (such as the World Wide Web's collection of webpages and URLs), or both (like the people and relationships that form a social network).

Complex networks are generally divided into four categories \citep{newmannetworks}:

@@

Trust is a concept studied in fields such as psychology and economics, with specific definitions.
In complex networks, under the perspective of computer science, it is a measure of one entity's confidence that another will behave properly and provide valid and/or meaningful data \citep{sherchan2013survey}.
What follows is the basis of how a network can be modelled using a graph and how a trust model can be applied to it.

@@

Another important aspect of trust in ad-hoc networks is that information is, generally, uncertain and incomplete \citep{baras2005cooperation}.
That is, since nodes form their own model and opinions of the surrounding network, it is unlikely that this data will be certain and accurate with reality.
For this reason, it is also possible to use data gathered by neighboring nodes to complement the model.
This data itself is subject to the trust evaluation of the neighbors, but it is crucial to better approximate the trust values of other nodes.
Incompleteness is an inherit trace of MANETs, since it is entirely possible for nodes to be too distant to communicate, and only occasionally come into contact.

>>>>

\chapter{Trust in Complex Networks}
\label{chap:complexnetworks}

@@

Complex networks can describe many systems which are observed in nature and society through a collection of \textit{vertices} (or \textit{nodes}) and \textit{edges} \citep{newmannetworks}.
They can be comprised of palpable components (such as computers and cables), somewhat abstract entities (such as the World Wide Web's collection of webpages and URLs), or both (like the people and relationships that form a social network).
Complex networks are generally divided into four categories \citep{newmannetworks}:

@@

Trust is a concept studied in fields such as psychology and economics, with specific definitions.
In complex networks, under the perspective of computer science, trust is a measure of how much confidence one member of a network has that another member of the same network will behave properly and provide valid and/or meaningful data \citep{sherchan2013survey}.
What follows is the basis of how a network can be modelled using a graph and how a trust model can be applied to it.

@@

Another important aspect of trust in ad-hoc networks is that information is, generally, uncertain and incomplete \citep{baras2005cooperation}.
That is, since nodes form their own model and opinions of the surrounding network, it is unlikely that this data will always be certain and accurate with reality.
For this reason, it is also possible to use data gathered by neighboring nodes to complement the model.
Data received from neighbors is also subject to the trust evaluation of whoever requests it, but it is crucial to have better knowledge about other members of the network.
Incompleteness is an inherit trace of MANETs, since it is entirely possible for nodes to be too distant to communicate, and only occasionally come into contact.
